The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-16 src/ms.tex
comment out section author

\secauthor{Adrian Price-Whelan}

@@

In addition to the two grants described above, the Project benefited from
a Gemini Observatory contract under its Science User Support Department,
which awarded funds for development work that supports both the Astropy and
DRAGONS\footnote{Data Reduction for Astronomy from Gemini Observatory North and
South (\url{https://github.com/GeminiDRSoftware/DRAGONS}).} projects. The
Project also received financial support from the Dunlap
Seed Funding program at the University of Toronto to develop educational
resources for scientific software packaging within the Learn Astropy
framework. The project also indirectly benefited from the NRAO ALMA Development
Study program, which supported the grant ``Linking CASA to the astropy
ecosystem''\footnote{\url{https://science.nrao.edu/facilities/alma/science_sustainability/Spectral_Cube_and_Radio_Beam_Ginsburg.pdf}}.
All of these successful proposals show that the \astropy Project
is vital for the astronomical infrastructure and community at large, and
strengthen its promising and sustainable future.

% ADD text for the new finance APE once it has a doi

>>>>

@@

In addition to the two grants described above, the Project benefited from
a Gemini Observatory contract under its Science User Support Department,
which awarded funds for development work that supports both the Astropy and
DRAGONS\footnote{Data Reduction for Astronomy from Gemini Observatory North and
South (\url{https://github.com/GeminiDRSoftware/DRAGONS}).} projects. The
Project also received financial support from the Dunlap
Seed Funding program at the University of Toronto to develop educational
resources for scientific software packaging within the Learn Astropy
framework. Moreover, the Project indirectly benefited from the NRAO ALMA Development
Study program, which supported the grant ``Linking CASA to the astropy
ecosystem''\footnote{\url{https://science.nrao.edu/facilities/alma/science_sustainability/Spectral_Cube_and_Radio_Beam_Ginsburg.pdf}}.
All of these successful funding proposals show that the \astropy Project
is vital for the astronomical infrastructure and community at large, and
strengthen its promising and sustainable future.

The Project follows a set of principles to fairly and effectively
distribute the above described funds. By drawing inspiration from
Numpy's NEP 48\footnote{https://numpy.org/neps/nep-0048-spending-project-funds.html},
the APE 19 \citep{ape19} document lays out these principles. We refer the
reader to that document for more details.
